### 2015-07-26 ms-thesis/ver2/intro/ms-thesis-intro.tex
-

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
df = pd.read_csv('../data/dji.csv',index_col='Date')
df['Adj Close'].head(100).plot()
plt.hold(False)
plt.hold(False)
plt.savefig(./intro/ms-thesis-intro_01.png)
plt.hold(False)
\end{minted}

@@

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
df = pd.read_csv('../data/ise.csv',index_col='Date')
df2 = df[df.index <'22-06-2000']
df2['Adj Close'].plot()
plt.hold(False)
plt.savefig(./intro/ms-thesis-intro_02.png)
plt.hold(False)
\end{minted}

@@

\begin{figure}[!hbp]
\center{
  \scalebox{0.30}{
  \includegraphics{./intro/volimkb.jpg}
  }
}
\caption{IMKB Volatility}
\vspace{0.6cm}
\end{figure}

>>>>

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
dji = pd.read_csv('../data/dji.csv',index_col='Date')
dji['Adj Close'].head(100).plot()
plt.hold(False)
plt.hold(False)
plt.savefig(./intro/ms-thesis-intro_01.png)
plt.hold(False)
\end{minted}

@@

\begin{minted}[fontsize=\footnotesize]{python}
import pandas as pd
ise = pd.read_csv('../data/ise.csv',index_col='Date')
ise2 = ise[df.index <'22-06-2000']
ise2['Adj Close'].plot()
plt.hold(False)
plt.savefig('ms-thesis-intro_02.png')
plt.hold(False)
\end{minted}

@@

\begin{minted}[fontsize=\footnotesize]{python}
ise2['Returns'] = ise2['Adj Close'].pct_change()
ise2.Returns.hist()
ise2.Returns.plot()
plt.hold(False)
plt.savefig('ms-thesis-intro_03.png')
plt.hold(False)
\end{minted}

%\includegraphics[height=6cm]{ms-thesis-intro_03.png}

\begin{figure}[!hbp]
\center{
  \scalebox{0.70}{
  \includegraphics{./intro/ms-thesis-intro_03.png}
  }
}
\caption{IMKB Volatility}
\vspace{0.6cm}
\end{figure}
